### 2017-07-19 architecture.tex
Fixing wording

To enable the definition and management of safe collection policies we
rely on a meta-policy model. The meta-policy model enables specification
of the policies described above. Each safe collection is associated with a steward
(or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema
is translated to a web-based form that can be completed by users during creation of a safe collection.
The defined policies (from the form or otherwise) is stored as a set of secure tags
on the collection's data storage bucket. The schema is enforced
by the various services that interact with the safe collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

@@

Export approvals are implemented as a policy associated with the collection's bucket.
\NAME ensures that the policy added is consistent with the meta-policy for the safe collection,
for example, ensuring that expiration for the policy
is within the duration specified on the safe collection.

>>>>

To enable the definition and management of safe collection policies we
rely on a meta-policy model. The meta-policy model enables specification
of the policies described above. Each safe collection is associated with a steward
(or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema
is translated to a web-based form that can be completed by administrators during the creation of a safe collection.
The defined policies (from the form or otherwise) is stored as a set of secure tags
on the collection's data storage bucket. The schema is enforced by the various services that interact
with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}

@@

Export approvals are implemented as copy operations between buckets. This usually is a copy from a
private safe-collection to a public safe-collection's bucket.
\NAME ensures that the export operation is consistent with the policies established for the originating
safe collection.
